### 2015-02-07 cav-2015-tex/rw.tex
Fixed typos.

Initial work on symbolic execution largely focused on checking
properties of imperative programs with primitive
types~\cite{Clarke:76,King:76}.
% Limitations of early symbolic execution techniques included non-primitive data types, path explosion and non-symbolic operations. Subsequent adaptations have sought to overcome these limitations.
Several projects have generalized the core idea of symbolic execution,
enabling it to be applied to programs with more general types,
including references and
arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. However, these
generalized symbolic execution (GSE) techniques work by branching over
multiple copies of the system state during dereferencing operations,
exacerbating path explosion
% and fragmenting the path condition. Producing a complete path
%condition for a single given control flow path would require merging
%an exponential number of states.
Our work leverages the core idea in generalized symbolic
execution with lazy initialization using on-the-fly reasoning to model
a black-box input heap during symbolic execution, but avoids the
nondeterminism introduced by GSE by constructing a single summary heap
and polynomially-sized path condition for each control flow path.

>>>>

Initial work on symbolic execution largely focused on checking
properties of imperative programs with primitive
types~\cite{Clarke:76,King:76}.
% Limitations of early symbolic execution techniques included non-primitive data types, path explosion and non-symbolic operations. Subsequent adaptations have sought to overcome these limitations.
Several projects have generalized the core idea of symbolic execution,
enabling it to be applied to programs with more general types,
including references and
arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. However, these
generalized symbolic execution (GSE) techniques work by branching over
multiple copies of the system state during dereferencing operations,
exacerbating path explosion.
% and fragmenting the path condition. Producing a complete path
%condition for a single given control flow path would require merging
%an exponential number of states.
Our work leverages the core idea in generalized symbolic
execution with lazy initialization using on-the-fly reasoning to model
a black-box input heap during symbolic execution, but avoids the
nondeterminism introduced by GSE by constructing a single summary heap
and polynomially-sized path condition for each control flow path.
